The Emergent Simplicity of Galaxy Size

### 2017-09-17 paper/galsize_paper.tex
Updated figure and caption

>>>>

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/cen_sat_sizes.pdf}
\caption{
{\bf Relative sizes of centrals and satellites.} In a narrow bin of halo mass $\mhalo=\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies. The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback halos"). In the fiducial model, galaxy size is set by the physical size of the virial radius at the time the (sub)halo attains its peak mass, naturally resulting in smaller sizes for satellites and backsplash centrals relative to true centrals of the same $\mpeak.$
}
\label{fig:shuffle}
\end{figure}
%-----------------------------------------------------------------------------------------------------
